### 2017-10-01 TF-vldb2018/subsec-Ginc.tex

\sstab{(1)} for some unit data update $\delta$ of $\Delta G$, where
(a) $\delta$ is an edge insertion/deletion, $(w_1,w_2)^+/(w_1,w_2)^-$ and $v$ in  both $\ball{[w_1,r]}$  and $\ball{[w_2,r]}$, or
(b) $\delta$ is a node insertion/deletion, $(w,(w,w'))^+$/$(w)^-$ and $v$ in $\ball{[w,r]}$; or

@@

\stitle{Correctness \& complexity analyses}. The correctness of \incd \wrt $\Delta G$ follows from Proposition~\ref{prop-affected-datainc} and the correctness of \incmatch and \comb.
\incd is overall in
$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx}\bigcup_{i\in[1,h]}$ $r|M(P_{fi}, \widehat{G\oplus\Delta G})|$+$r|P||\affballsx|)$ time \wrt $\Delta G$, while $r$ is small, \ie 2 or 3  (See~\cite{fullvldb18}).
\looseness=-1

@@

Algorithm \inc is able to handle {\em simultaneous} $\Delta P$ and $\Delta G$, because of the consistency in:
(1) the processes for handling $\Delta P$ and $\Delta G$, which follow the same steps in Section~\ref{sec-dynamictopk};
(2) auxiliary data structures for supporting $\Delta P$ and $\Delta G$; and
(3) the combination procedures, which suffice to support simultaneous pattern and data updates.

@@

%\vspace{0.5ex}
\stitle{Remark}. Note that the running time of \incp and \incd is determined by \{$P, \Delta P, \tilde{M}(P,G)$, $\affballsx$\}
and \{$P, \tilde{M}(P,G)$, $\affballsx$\}, respectively, not directly depending on $G$.
From this, we complete the proof of Theorem~\ref{thm-framework-inc}.

>>>>

\sstab{(1)} for some unit data update $\delta$ of $\Delta G$, where
(a) $\delta$ is an edge insertion/deletion, $(w_1,w_2)^+/(w_1,w_2)^-$ and $v$ is in  both $\ball{[w_1,r]}$  and $\ball{[w_2,r]}$, or
(b) $\delta$ is a node insertion/deletion, $(w,(w,w'))^+$/$(w)^-$ and $v$ is in $\ball{[w,r]}$; or

@@

\stitle{Correctness \& complexity analyses}. The correctness of \incd \wrt $\Delta G$ follows from Proposition~\ref{prop-affected-datainc} and the correctness of \incmatch and \comb.
\incd is overall in
$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx}\bigcup_{i\in[1,h]}$ $r|M(P_{fi}, \widehat{G\oplus\Delta G})|$+$r|P||\affballsx| + |\Delta G|)$ time \wrt $\Delta G$, while $r$ is small, \ie 2 or 3  (See~\cite{fullvldb18}).
\looseness=-1

@@

Algorithm \inc is able to handle {\em simultaneous} $\Delta P$ and $\Delta G$, because of the consistency in:
(1) the processes for handling $\Delta P$ and $\Delta G$, which follow the same steps in Section~\ref{subsec-framework};
(2) auxiliary data structures for supporting $\Delta P$ and $\Delta G$; and
(3) the combination procedures, which suffice to support simultaneous pattern and data updates.

@@

%\vspace{0.5ex}
\stitle{Remark}. Note that the running time of \incp and \incd is determined by \{$P, \Delta P, \tilde{M}(P,G)$, $\affballsx$\}
and \{$P, \Delta G, \tilde{M}(P,G)$, $\affballsx$\}, respectively, not directly depending on $G$.
From this, we complete the proof of Theorem~\ref{thm-framework-inc}.
